%! TeX root: ../main.tex
\noindent \underline{\textbf{Problem 1.}} Let \( S \) be the set of all closed cubes in \( \mathbb{R}^{d}  \), \( S' \) be the set of all open cubes in \( \mathbb{R}^{d}  \), and \( S'' \) be the set of all rectangles \( R \) such that for some \( a_1 < b_1, \cdots , a_d < b_d \in \mathbb{R}^{d}  \), \[(a_1, b_1) \times \cdots \times (a_d,b_d) \subseteq R \subseteq [a_1, b_1] \times \cdots \times [a_d,b_d].\] For every set \( A \subseteq \mathbb{R}^{d}  \), let \( m_*(A), \ m'_*(A), \  \) and \( m''_*(A) \) be defined as: \[ m_*(A) \coloneqq \inf \sum_{k=1}^{\infty} \mbox{vol}(Q_k), \ m'_*(A) \coloneqq \inf \sum_{k=1}^{\infty}\mbox{vol}(Q_k'), \mbox{ and } m''_*(A) \coloneqq \inf \sum_{k=1}^{\infty} \mbox{vol}(R_k),\] where the infima are taken over all counter coverings of \( A \) by \( Q_k \in S \), \( Q_k' \in S' \), and \( R_k \in S'' \) respectively. Prove that \( m''_*(A) = m'_*(A) = m_*(A) \).

\noindent As is granted on the assignment sheet, we will use the following facts about rectangles without proof:
\begin{enumerate}
	\item For every rectangle \( R \) and \( \varepsilon > 0 \), there exists an open rectangle \( R_\varepsilon  \) such that \( R \subseteq R_\varepsilon  \) and \( \mbox{vol}(R_\varepsilon ) \leq \mbox{vol}(R) + \varepsilon  \). Likewise, for every cube \( Q \) and \( \varepsilon > 0 \), there exists an open cube \( Q_\varepsilon  \) such that \( Q \subseteq Q_\varepsilon  \) and \( \mbox{vol}(Q_\varepsilon ) \leq \mbox{vol}(Q) + \varepsilon  \).
	\item Every open rectangle \( R \) can be written as \( R = \bigcup_{k=1}^{\infty} Q_k \) for some cubes \( Q_k \in S \) whose interiors are disjoint.
	\item If a sequence of disjoint rectangles \( (R_k)_{k \geq 1}  \) is such that for some rectangle \( R \), \( \bigcup_{k=1}^{\infty} R_k \subseteq R \), then \( \sum_{k=1}^{\infty} \mbox{vol}(R_k) \leq \mbox{vol}(R) \).	
	
	
\end{enumerate}
\begin{proof} Let \( A \subseteq \mathbb{R}^{d}  \) be arbitrary. We note that it suffices to show that \( m''_*(A) \leq m'_*(A) \leq m_*(A) \leq m''_*(A)\), since \( m_*''(A) \leq m'_*(A), m_*(A) \leq m''_*(A) \implies m'_*(A) = m''_*(A) \) and \( m_*(A) = m''(A) \implies m'_*(A) = m_*(A) \implies m''_*(A) = m'_*(A) = m_*(A). \)

Suppose, for 1 - 3 below, that the exterior measure on the left-hand-side of the inequality is finite. We prove the infinite cases below.

\noindent \underline{\textbf{1. \( m_*''(A) \leq m'_*(A) \)}} Suppose \( m_*'(A) < \infty  \), otherwise there is nothing to prove.

\noindent We define the following sets:
\[ R \coloneqq \Set{\sum_{k = 1}^{\infty} \mbox{vol}(R_k) | A \subseteq \bigcup_{k=1}^{\infty} R_k, R_k \in S''  } \mbox{ and } C \coloneqq  \Set{\sum_{k = 1}^{\infty} \mbox{vol}(Q'_k) | A \subseteq \bigcup_{k=1}^{\infty} Q'_k, Q'_k \in S'  }. \] Notice that \( C \subseteq R \); to see why, let \( x \in C \) be arbitrary. Hence there exists some sequence of open cubes \( (C_k : k \geq 1, C_k \in S') \) such that \( A \subseteq \bigcup_{k=1}^{\infty} C_k \) and \( x = \sum_{k=1}^{\infty} \mbox{vol}(C_k)  \). But then, by the construction of \( S'' \), it follows that each open cube \( C_k \in S'' \) (since open cubes are indeed rectangles). From this realisation, we obtain that \( x \in R \) as it meets the necessary criteria (namely that \( A \subseteq \bigcup_{k=1}^{\infty} C_k \mbox{ and } C_k \in S''  \) for each \( k \geq 1 \)). Hence we have \( C \subseteq R \implies m_*'(A) =  \inf C \geq \inf R = m''_*(A) \) (cf. Lemma 1.1). Hence, \( m''_*(A) \leq m'_*(A) \), as needed.

\noindent \underline{\textbf{2. \( m'_*(A) \leq m_*(A) \)}} Suppose \( m_*(A) < \infty  \), otherwise there is nothing to prove.


We commence this portion of the proof by noting that the volume of a closed cube equals that of its interior by definition. To see this, we use the following argument:
\begin{itemize}
	\item Firstly, if \( C = [a, b] \times \cdots \times [a, b] \in S \) is a closed cube in \( \mathbb{R}^{d}  \) (where \( a < b \)), we note that its interior \( C^{o} = (a,b) \times \cdots \times (a,b). \) To see this, let \( x \in C^{o} \), then there exists an \( r > 0 \) such that \( V_r(x) \subseteq C \). Obviously, \( x \neq a  \) and \( x \neq b \), since these are boundary points of \( C \), hence \( x \in  (a,b) \times \cdots \times (a,b)  \subseteq C\), since this is an open set and \( C^{o} \subseteq C  \). Now if \( x \in  (a,b) \times \cdots \times (a,b) \implies x \in C^{o}  \), as this is an open subset of \( C \). Hence, the interior of a closed cube is an open cube.
	\item By the definition of a rectangle, then, we must have that \( \mbox{vol}(C) = \mbox{vol}([a,b] \times \cdots \times [a,b]) = (b-a)^{d} = \mbox{vol}((a,b) \times \cdots \times (a,b)) =    \mbox{vol}(C^{o} ).    \) 
\end{itemize}
Using this argument, let \( (C_k : k \geq 1, C_k \in S )\) be a sequence of closed cubes such that \( A \subseteq \bigcup_{k=1}^{\infty} C_k \). Then, by the argument above, we obtain \[\sum_{k=1}^{\infty} \mbox{vol}(C_k) = \sum_{k=1}^{\infty}\mbox{vol}(C_k^{o} ).  \tag{1.2.1} \] So if \( k \coloneqq m_*(A)\) (provided that its finite, otherwise there is nothing to prove) and \(\varepsilon > 0 \) is arbitrary, by definition of the infimum, there exists some covering of \( A \subseteq \bigcup_{k=1}^{\infty}Q_k \) by closed cubes \( Q_k \) such that \[\sum_{k=1}^{\infty}\mbox{vol}(Q_k) < k + \varepsilon  = m_*(A) + \varepsilon . \] But then we have that \( m_*'(A) \leq \sum_{k=1}^{\infty}\mbox{vol}(Q_k^{o}) = \sum_{k=1}^{\infty}\mbox{vol}(Q_k) < m_*(A) + \varepsilon    \) . Since we can achieve this result for arbitrary \( \varepsilon > 0 \), we conclude that \( m_*'(A) \leq m_*(A) \), as required.


\noindent \underline{\textbf{3. \( m_*(A) \leq m_*''(A).\)}} Suppose that \( m_*(A) < \infty \), otherwise there is nothing to prove.

Let \( \{ R_k : R_k \in S'' \}_{k=1}^{\infty}  \) be a sequence of rectangles in \( \mathbb{R}^{d}  \) such that \(A \subseteq \bigcup_{k=1}^{\infty} R_k. \) By fact 1, for each rectangle \( R_k \) and \( \varepsilon >0  \) there exists an open rectangle \( R_{k ,\varepsilon }  \) such that \( R_k \subseteq R_{k, \varepsilon }  \) and \( \mbox{vol}(R_{k,\varepsilon } ) \leq \mbox{vol}(R_k) + \frac{\varepsilon }{2^{k} } 	 \). Therefore, \[A \subseteq \bigcup_{k=1}^{\infty} R_k \subseteq \bigcup_{k=1}^{\infty} R_{k,\varepsilon }.\] By fact 2, since each \( R_{k,\varepsilon }  \) is open, there exists a sequence \( \{ C_{k,j,\varepsilon }  : C_{k,j,\varepsilon }  \in S \}_{j=1}^{\infty}   \) of closed cubes whose interiors are pairwise disjoint and for which \( R_{k, \varepsilon } = \bigcup_{j=1}^{\infty} C_{k,j,\varepsilon } .\) It hence follows that \[ \bigcup_{j=1}^{\infty} C_{k,j,\varepsilon } ^{o} \subseteq \bigcup_{j=1}^{\infty} C_{k,j,\varepsilon } = R_{k,\varepsilon },   \] where \( A^{o}  \) denotes the interior of a set \( A \). Fact 2 assures that the interiors of the closed cubes \( C_{k,j,\varepsilon }  \) are pairwise disjoint, hence, by fact 3, we must have that \[\sum_{j=1}^{\infty}\mbox{vol}(C^{o}_{k,j,\varepsilon }  ) \leq \mbox{vol}(R_{k,\varepsilon } ) , \] but then by (1.2.1) above, we obtain \[\sum_{j=1}^{\infty}\mbox{vol}(C_{k,j,\varepsilon } ) =\sum_{j=1}^{\infty}\mbox{vol}(C^{o}_{k,j,\varepsilon }  ) \leq \mbox{vol}(R_{k,\varepsilon } ) \leq \mbox{vol}(R_k) + \frac{\varepsilon }{2^{k} } .\] Summing over all \( k \), we have found a covering by closed cubes which admits a sum of volumes less than or equal to that of our arbitrary covering by rectangles: \[\sum_{k=1}^{\infty} \sum_{j=1}^{\infty}\mbox{vol}(C_{k,j,\varepsilon } ) \leq \sum_{k=1}^{\infty}\left ( {\mbox{vol}(R_k) + \frac{\varepsilon }{2^{k} } } \right ) = \sum_{k=1}^{\infty}\mbox{vol}(R_k) + \varepsilon . \]  
Since \( \varepsilon  \) and the covering by rectangles was arbitrary, we can conclude the following: for a given \( \varepsilon > 0 \), there exists a covering by rectangles of \( A \subseteq \bigcup_{k=1}^{\infty} Q_{k} '' \), where \( Q_k'' \in S'' \), such that \[ \sum_{k=1}^{\infty} \mbox{vol}(Q''_k) < m''_*(A) + \varepsilon. \] Now, we have shown that we can find a covering by closed cubes of \( A \subseteq \bigcup_{k=1}^{\infty} Q_k \), where \( Q_k \in S \) for which \[\sum_{k=1}^{\infty} \mbox{vol}(Q_k) \leq \sum_{k=1}^{\infty}\mbox{vol}(Q''_k) < m''_*(A) + \varepsilon . \] Hence, for arbitrary \( \varepsilon >0 \), we obtain \(m_*(A) \leq \sum_{k=1}^{\infty}\mbox{vol}(Q_k) 	  \leq m_*''(A)+\varepsilon \); hence, sending \( \varepsilon \to 0 \), we obtain, as required, that \( m_*(A) \leq m_*''(A) \).

As previously stated, inequalities 1, 2, and 3 imply that for a set \( A \subseteq \mathbb{R}^{d}  \), \( m_*(A) = m_*'(A) = m_*''(A) \), thereby completing the proof.
\end{proof}
\begin{proof}[Lemma 1.1]
\emph{For sets \( A, \subseteq \mathbb{R}^{d}  \) with \( A \subseteq B \), we have \( \inf B \leq \inf A \).}
This lemma is proven trivially. Note that \( A \subseteq B \) implies that for any \( a \in A \) there exists a \( b \in B \) with \( b \leq a \). Let \( \varepsilon > 0 \) be arbitrary. Then there exists a \( y_A \in A \) (and hence a corresponding \( y_B \in B : y_B \leq y_A \)) such that \[\inf B \leq y_B \leq y_A < \inf A + \varepsilon.\] Sending \( \varepsilon  \to 0 \) implies that \( \inf B \leq \inf A \) as needed.
\end{proof}

\noindent \textbf{Infinite case 1.} Suppose \( m_*''(A) = \infty  \). We must show that \( m_*'(A) = \infty  \). This means that for every covering of \( A \) by a sequence of rectangles \( \{ R_k : R_k \in S''\}_{k=1}^{\infty}  \), \[\sum_{k=1}^{\infty}\mbox{vol}(R_k) = \infty.\] Suppose towards contradiction that there is some covering of \( A \) by a sequence of open cubes \( \{ C'_k : C'_k \in S'  \}_{k=1}^{\infty}    \) such that \(\sum_{k=1}^{\infty}\mbox{vol}(C'_k) < \infty. \) But this is an immediate contradiction, since we would have some covering of \( A \) by rectangles (since open cubes are rectangles) that is finite, hence \( m_*'(A) = \infty  \) as needed. \\


\noindent \textbf{Infinite case 2.} Suppose \( m_*'(A) = \infty  \). We must show that \( m_*(A) = \infty. \) This means that for every covering of \( A \) by a sequence of open cubes \( \{ C_k' : C_k' \in S' \}_{k=1}^{\infty}    \), we have \[\sum_{k=1}^{\infty}\mbox{vol}(C'_k) = \infty. \] Suppose towards contradiction that there is some sequence of closed cubes \( \{ C_k : C_k \in S\}_{k=1}^{\infty}    \) such that \( \sum_{k=1}^{\infty}\mbox{vol}(C_k) < \infty .\) But, as argued in (2), there is a corresponding sequence of open cubes (namely the interiors) such that \sum_{k=1}^{\infty}\mbox{vol}(C_k) = \sum_{k=1}^{\infty}\mbox{vol}(C_k^{o} ) < \infty\), a contradiction to the hypothesis that every covering by open cubes leads to an infinite sum of volumes. Thus, it follows that \( m_*(A) = \infty \), as required.    \\

\noindent\textbf{Infinite case 3.} Suppose \( m_*(A) = \infty \). We must show that \( m_*''(A) = \infty  \). This means that for every covering of \( A \) by a sequence of closed cubes \( \{ C_k : C_k \in S \} _{k=1} ^{\infty}  \), we have \( \sum_{k=1}^{\infty}\mbox{vol}(C_k) = \infty. \) Suppose towards contradiction that there exists a covering of \( A \) by a sequence of rectangles \( \{ R_k : R_k \in S'' \}_{k=1} ^{\infty}   \) such that \( \sum_{k=1}^{\infty}\mbox{vol}(R_k) < \infty \). Yet as argued in (3), we can construct a sequence of closed cubes \( \{ C_k : C_k \in S \}_{k=1} ^{\infty}  \) such that \( \sum_{k=1}^{\infty}\mbox{vol}(C_k) \leq \sum_{k=1}^{\infty}\mbox{vol}(R_k) \implies \sum_{k=1}^{\infty}\mbox{vol}(R_k) = \infty   \), a contradiction. Hence, it follows as well that \( m_*''(A) = \infty  \), as needed.
